Capon Beamforming Applied on Moving Objects - An Analysis of Local Lateral Shift-Invariance

### 2013-12-04 HRUIofMovingObjects/jrnl_article.tex
Moving object: writing

In \cite{Cox1973}, Cox derives formulas for the resolution of the Capon beamformer, and presents in great detail how the amount of mismatch between the selected steering vector and the signal propagation vector impacts the beamformer output in simple situations. Cox states the following important fact about the Capon beamformer (the $\vec{k}_3$ processor): 
\begin{quote}
"\textit{... a $\vec{k}_3$ processor requires more closely spaced beams than a ... $\vec{k}_1$-processor in order to avoid serious signal suppression effects being introduced on signals arriving from directions between the beams}", 
\end{quote}
where $\vec{k}_1$ is the delay-and-sum (DAS) beamformer. In Fig.\,\ref{fig:das_capon_beams} we have plotted the two-way response for DAS and the Capon beamformer using (26) and (32) in \cite{Cox1973}. A 64-element linear array with $\lambda/2$ element spacing, where $\lambda$ is the wavelength, is scanned over a sector equal to two times the two-way system resolution ($1/64$ radians) using a narrow band pulse. Located in the farfield of the sector is an object moving parallel to the array surface. The plot shows the scanned output when the object is located at plus and minus half the system resolution. No spatially white noise is present. Hence, the interference-noise matrix ($\sigma_0^2\mat{Q}$ in \cite{Cox1973}) is the identity. The effect of typical subarray averaging and diagonal loading ($L=32$ and $d=1/100$) has also been added to the Capon beamformer output. A diagonal loading of $1/100$ corresponds to an signal-to-noise ratio of 20 dB before array gain is applied. The figure shows that a DAS beamformer, with a beamspacing equal to the system resolution, could yield a 1.9 dB scalloping loss \cite{Harris1978} if the object is moving parallel to the array. However if the Capon beamformer is used with the same beam density the scalloping loss could be as large as $27$ dB.

\begin{figure}[!t]
\centerline{
\includegraphics[width=\linewidth]{\img fig1_2way.eps}
}
\caption{Theoretical drop in output power mid-way between receive beams for delay-and-sum and Capon beamforming ($M=64$, $L=32$, $d=0.01$) applied in a farfield-narrowband setting. The scanned output from both beamformers is plotted for two different time instances. For the first instances an object is located in the farfield of the scanned sector at an angle equal to half the system resolution, and for the latter the object is moved a distance corresponding to the system resolution.}
\label{fig:das_capon_beams}
\end{figure}

@@

\section{Discussion}\label{sec:dis}
\comment{work in progress}
In this paper we have investigated the lateral shift-invariance property of the Capon beamformer when imaging moving objects. In Section \ref{sec:capon_LLSI} it was shown that a Capon beamformer with high resolution parameters is not locally laterally shift-invariant when subjected to motion. In Section \ref{sec:methods} we therefore presented methods for improved shift-invariance. The most promising oversampling method, with respect to improved shift-invariance, reduction in acquisition frame rate and processing complexity, was based on phase rotation. In Section \ref{sec:res} we presented results showing that this method also works on \textit{in-vitro} data.

@@

>>>>

In \cite{Cox1973}, Cox derives formulas for the resolution of the Capon beamformer, and presents in great detail how the amount of mismatch between the selected steering vector and the signal propagation vector impacts the beamformer output in simple situations. Cox states the following important fact about the Capon beamformer (the $\vec{k}_3$ processor): 
\begin{quote}
"\textit{... a $\vec{k}_3$ processor requires more closely spaced beams than a ... $\vec{k}_1$-processor in order to avoid serious signal suppression effects being introduced on signals arriving from directions between the beams}", 
\end{quote}
where $\vec{k}_1$ is the delay-and-sum (DAS) beamformer. In Fig.\,\ref{fig:das_capon_beams} we have plotted the two-way response for DAS and the Capon beamformer using (26) and (32) in \cite{Cox1973}. A 64-element linear array with $\lambda/2$ element spacing, where $\lambda$ is the wavelength, is scanned over a sector equal to two times the two-way system resolution ($1/64$ radians) using a narrow band pulse. Located in the farfield of the sector is an object moving parallel to the array surface. The plot shows the scanned output when the object is located at plus and minus half the system resolution. No spatially white noise is present. Hence, the interference-noise matrix ($\sigma_0^2\mat{Q}$ in \cite{Cox1973}) is the identity. The effect of typical subarray averaging and diagonal loading ($L=32$ and $d=1/100$) has also been added to the Capon beamformer output. A diagonal loading of $1/100$ corresponds to an signal-to-noise ratio of 20 dB before array gain is applied. The figure shows that a DAS beamformer, with a beamspacing equal to the system resolution, could yield a 1.9 dB scalloping loss \cite{Harris1978} if the object is moving parallel to the array. However if the Capon beamformer is used with the same beam density the scalloping loss could be as large as $27$ dB. To get the scalloping loss for the Capon beamforming smaller than 1.9 dB for this specific example the angular displacement has to reduced with a factor 27.

\begin{figure}[!t]
\centerline{
\includegraphics[width=\linewidth]{\img fig1_2way.eps}
}
\caption{Theoretical drop in output power mid-way between receive beams for delay-and-sum and Capon beamforming ($M=64$, $L=32$, $d=0.01$) applied in a farfield-narrowband setting. The scanned output from both beamformers is plotted for two different time instances. For the first instances an object is located in the farfield of the scanned sector at an angle equal to half the system resolution, and for the latter the object is moved an angular distance corresponding to the system resolution.}
\label{fig:das_capon_beams}
\end{figure}

@@

\section{Discussion}\label{sec:dis}
\comment{work in progress}
In this paper we have investigated the lateral shift-invariance property of the Capon beamformer when imaging moving objects. In Section \ref{sec:capon_LLSI} it was shown that a Capon beamformer with high resolution parameters is not locally laterally shift-invariant when subjected to motion. \comment{Skriv hva som skapte shift invariansen} In Section \ref{sec:methods} we therefore presented methods for improved shift-invariance. The most promising oversampling method, with respect to improved shift-invariance, reduction in acquisition frame rate and processing complexity, was based on phase rotation. In Section \ref{sec:res} we presented results showing that this method also works on \textit{in-vitro} data.

@@

\comment{Discuss the findings by Cox. 47 dB SNR equals 10x higher resolution. Explaine the difference betweeen one moving point scatterer and the problem of resolving two closely spaced point scatterers.}
